\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-10-31 lang-design.tex
reminder to myself
Some Comments.

In \cref{fig:stlc-mechanized}, just because the "typesafe" theorem in
"STLC" is inherited and reused by "STLCFix", it does not follow that
in "STLCFix" the programmer can use "typesafe" to prove "progress".
If the programmer did, then they would be committing the logical fallacy
of circular reasoning: the proof of "progress" would depend on "typesafe",
yet the proof of "typesafe" depends on "progress".
%
Such circularity would easily lead to logical inconsistency:

@@

Note that the requirement still allows a derived family to introduce
new declarations into the context of a field.
For example, the left column of \cref{fig:stlc-isorec-prod} shows an
extension of STLC with iso-recursive types, where "tysubst" is
introduced into the context of "hasty".

@@

\noindentparagraph{Composing families.}

>>>>

In \cref{fig:stlc-mechanized}, just because the "typesafe" theorem in
"STLC" is inherited and reused by "STLCFix", it does not follow that
in "STLCFix" the programmer can use "typesafe" to prove "progress".
If the programmer did, then they would be committing the logical fallacy
of circular reasoning: the proof of "progress" would depend on "typesafe",
yet the proof of "typesafe" depends on "progress".
%
Such circularity would easily lead to logical inconsistency:
\YZ{Mention non-exhaustivity/overriding already poses challenges to ensuring consistency.}

@@

Note that the requirement still allows a derived family to introduce
new declarations into the context of a field. \EDJ{Maybe a better wording is ``the relative order between fields are preserved during inheritance''?}
For example, the left column of \cref{fig:stlc-isorec-prod} shows an
extension of STLC with iso-recursive types, where "tysubst" is
introduced into the context of "hasty".

@@

\noindentparagraph{Composing families.} \EDJ{I feel this paragraph will cause more confusion---because it is inheritance judgement/linkage transformer being mixed in, not family itself. Conceptually not distinguishing family and linkage transfomer will make reader wonder what this magic black box here actually is}
